The Concurrent Calculi Formalisation Benchmark

### 2023-10-12 challenges/coinduction.tex
Fix description of coinduction challenge.

For this challenge, we adopt a fragment of the untyped $\pi$-calculus
that includes process replication.
% The setting for this challenge is an untyped calculus of
% communicating systems with replication of processes, the syntax and
% semantics of which are presented below.
The objective of this challenge is to prove that strong barbed
bisimilarity
% for this calculus
is an equivalence relation. Which, to reiterate, entails the use of
coinduction due to the presence of infinite behaviour.

>>>>

For this challenge, we adopt a fragment of the untyped $\pi$-calculus
that includes process replication.
% The setting for this challenge is an untyped calculus of
% communicating systems with replication of processes, the syntax and
% semantics of which are presented below.
The objective of this challenge is to prove a context lemma for strong barbed congruence.
The context lemma establishes that processes are strong barbed congruent if and only if the processes obtained by applying a substitution to them and composing them with an arbitrary process are strongly barbed bisimilar.
Which, to reiterate, entails the use of coinduction due to the presence of infinite behaviour.

### 2023-10-12 paper/paper.tex
Fix description of coinduction challenge.

\subsection{Coinduction}
Our \textbf{coinduction challenge} (Appendix~\ref{sec:challenge:coinduction}) is to prove that \emph{strong barbed bisimilarity} is a congruence for a limited calculus with (infinite) replication of processes.
The key issue of this challenge is the coinductive reasoning about the infinite behaviours of the replication operator.

>>>>

\subsection{Coinduction}
Our \textbf{coinduction challenge} (Appendix~\ref{sec:challenge:coinduction}) is to prove a context lemma involving \emph{strong barbed congruence} for a limited calculus with (infinite) replication of processes.
The key issue of this challenge is the coinductive reasoning about the infinite behaviours of the replication operator.
